\documentclass[11pt]{article}
\usepackage[T1]{fontenc}

\usepackage{newtxtext,newtxmath}  % Change font to Times New Roman
\usepackage{fontawesome}  % Icons
\usepackage{titlesec}  % Section format
\usepackage{geometry}  % Page layout
\usepackage{enumitem}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{xparse}  % for \NewDocumentCommand
\usepackage{ifthen}  % for \ifthenelse and \equal

\titleformat{\section}{\sc\Large}{}{0pt}{}[\hrule]
\titlespacing*{\section}{0pt}{0.7em minus 0.2em}{0.8em minus 0.2em}
\titleformat{\subsection}{\bfseries}{}{0pt}{}[]
\titlespacing*{\subsection}{0pt}{1em plus 0.2em minus 0.2em}{0.5em plus 0.2em minus 0.2em}
\titlespacing{\paragraph}{0pt}{0.5\baselineskip}{1em}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\geometry{centering,left=2cm,right=2cm,top=1.5cm,bottom=2cm}

\setitemize{topsep=0.1em,partopsep=0em,itemsep=0.1em,parsep=0em,leftmargin=1em}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=blue,
}

\newcommand{\leftrighttext}[2]{%
  \makebox[\textwidth][l]{#1\hfill#2}%
}
\newcommand*{\cventry}[6]{%
  \leftrighttext{%
    {\large\bfseries#1}%
    \ifthenelse{\equal{#2}{}}{}{, \textit{#2}}%
    \ifthenelse{\equal{#3}{}}{}{, #3}%
    \ifthenelse{\equal{#4}{}}{}{, #4}%
    \strut%
  }{#5}
  \newline{}
  \begin{minipage}[t]{\linewidth}#6
  \end{minipage}
}

\NewDocumentCommand{\cvitem}{O{0.13\textwidth} O{.1em} m m}{%
  \begin{tabular}{@{}p{#1}@{\hspace{0.01\textwidth}}p{\dimexpr\textwidth-#1-0.01\textwidth\relax}@{}}%
    \raggedleft{#3} &{#4}%
  \end{tabular}%
\par\addvspace{#2}}
\newcommand{\cvpublist}[3]{
  \cvitem{#1}{%
    {\bfseries{#2} \vspace*{0.2em}}\newline{}
    \begin{minipage}[t]{\linewidth}{\normalsize #3 \vspace*{3pt}}
    \end{minipage}%
  }
}
\newcommand{\cvshortlist}[2]{\cvitem[0.15\textwidth][0em]{#1}{#2}}

\begin{document}

\setlength{\tabcolsep}{0.4em}
\newcommand{\comma}{\hspace*{0.3em}}
\begin{tabular}{lclclcl}
  \multicolumn{2}{l}{\LARGE \textbf{\textsc{Yifan Zhao}}} \vspace{0.4em} \\
  \faEnvelope\comma\href{mailto:yifanz16@illinois.edu}{yifanz16@illinois.edu}
  & $\cdot$ & \faLink\comma\url{https://evzh.net}
  & $\cdot$ & \faLinkedin\comma
  \href{https://www.linkedin.com/in/yifan-zhao-287745162/}{yifan-zhao-287745162}
  & $\cdot$ & \faPhone\comma{}{(810) 333-7919}
\end{tabular}
\vspace{0.3em}

\section{Research Interests}
Machine Learning Systems and Compilers;
Compiler Design and Optimizations;
Performance Engineering; Approximate Computing; Edge Computing.

\section{Research and Work Experience}

\cventry{University of Illinois Urbana-Champaign}{}{Urbana}{IL}{2019 --- 2026
(planned)}
{
  Graduate Research Assistant, Ph.D.~candidate in Computer Science
  \begin{itemize}
    \item Designed and build tensor compilers that optimize DNN inference on GPUs, CPUs,
      and accelerators.
    \item Developed the \href{https://arxiv.org/abs/2510.08726}{Neptune} tensor compiler:
      generalizes and automates FlashAttention-style operator fusion;
      achieves SOTA performance on modern GPUs.
    \item Developed the \href{https://dl.acm.org/doi/10.1145/3620666.3651348}{Felix}
      tensor program autotuner: create a differentiable search space for tensor programs,
      and optimize them with gradient descent.
    \item Published first-author papers at top ML systems conferences:
      \href{https://pldi26.sigplan.org/program/program-pldi-2026/}{Neptune [PLDI'26]},
      \href{https://dl.acm.org/doi/10.1145/3620666.3651348}{Felix [ASPLOS'24]},
      \href{https://proceedings.mlsys.org/paper_files/paper/2023/file/89efa87dc8f0a5d18e4ae0a479658f60-Paper-mlsys2023.pdf}{ApproxCaliper
      [MLSys'23]}.
  \end{itemize}
}

\cventry{Nvidia}{Deep Learning Engineer Intern}{Santa Clara}{CA}{May 2024 --- Aug.~2024}
{
  \begin{itemize}
    \item Helped develop loop optimizations for an internal DL compiler
      (polyhedral transformations in MLIR).
    \item Implemented complex DNN operators (e.g., deformable convolution/attention) in
      this compiler
      to probe missing features and performance issues, and deliver usable kernels.
    \item Wrote an internal paper documenting the improvements.
\end{itemize}}

\cventry{University of Michigan}{Undergraduate Research Assistant}{Ann Arbor}{MI}{May
2018 --- Sep.~2018}
{
  \begin{itemize}
    \item Co-led the Huron project: a compiler analysis and runtime for detecting and repairing
      false sharing (performance bug) in parallel CPU programs.
    \item Published a co-first-author paper on Huron at
      \href{https://dl.acm.org/doi/10.1145/3314221.3314644}{PLDI'19}.
  \end{itemize}
}

\section{Education}

\cventry{University of Illinois Urbana-Champaign}{}{Urbana}{IL}{2019 --- Now}
{\textit{Ph.D.~candidate} in Computer Science; \textbf{Advisors}: Sasa Misailovic, Vikram Adve \\
  Selected courses: Advanced Compiler Design, Compilers for Edge Computing, ML for Software
Engineering}

\cventry{University of Michigan}{}{Ann Arbor}{MI}{2017 --- 2019}
{\textit{Bachelor of Science and Engineering} in Computer Science \\
Awards: James B. Angell Scholar, University Honors, Dean’s Honor List}

\cventry{Shanghai Jiaotong University}{}{Shanghai}{China}{2015 --- 2019}
{\textit{Bachelor of Science} in Electrical and Computer Engineering \\
Shanghai Jiaotong --- Univ.~of Michigan Dual Degree Program}

\section{Technical Skills}

\begin{itemize}
  \item Areas of expertise: compilers (deep learning and general-purpose),
    programming languages, system design, performance engineering
  \item Compilers: LLVM; TVM, MLIR; Triton, JAX Pallas, TileLang
  \item Deep learning frameworks: PyTorch (incl.~TorchInductor), JAX; CUTLASS
  \item Programming languages: Python, C/C++, CUDA, Rust (working languages); also familiar with
    Haskell, C\#, JavaScript.
\end{itemize}

\section{Select Publications}

\cvpublist{[PLDI'26]}
{Neptune: Advanced ML Operator Fusion for Locality and Parallelism on GPUs.}
{\textbf{Yifan Zhao}, Egan Johnson, Prasanth Chatarasi, Vikram Adve, Sasa Misailovic}

\cvpublist{[Under review \\ASPLOS'27]}
{Nautilus: Auto-Scheduling Tensor Compiler for Advanced Fusion in Asynchronous
and Pipelined GPU Kernels.}
{\textbf{Yifan Zhao}, Yuchen Yang, Matei Budiu, Sasa Misailovic}

\cvpublist{[ISSTA'26]}
{\mbox{ARQ: A Mixed-Precision Quantization Framework for Accurate and Certifiably Robust
DNNs.}\vspace{-1em}}
{Yuchen Yang, \textbf{Yifan Zhao}, Shubham Ugare, Gagandeep Singh, Sasa Misailovic}

\cvpublist{[ASPLOS'24]}
{Felix: Optimizing Tensor Programs with Gradient Descent.}
{\textbf{Yifan Zhao}, Hashim Sharif, Vikram Adve, Sasa Misailovic}

\cvpublist{[PACMI'24]}
{\mbox{Programming Systems for Improving the Performance of Deep Learning-Intensive
Applications.}\vspace{-1em}}
{\textbf{Yifan Zhao}, Vikram Adve, Sasa Misailovic}

\cvpublist{[MLSys'23]}
{\mbox{ApproxCaliper: Exploiting Application-level Error Resiliency for Optimizing Neural
Networks.}\vspace{-1em}}
{\textbf{Yifan Zhao*}, Hashim Sharif*, Peter Pao-Huang, Vatsin Ninad Shah, Arun
  Narenthiran, Mateus Valverde Gasparino, Nathan Zhao, Abdulrahman Mahmoud, Sarita Adve,
Girish Chowdhary, Sasa Misailovic, Vikram Adve}

\cvpublist{[VR'23]}
{Power, Performance, and Image Quality Tradeoffs in Foveated Rendering.}
{Rahul Singh, Muhammad Huzaifa, Jeffrey Liu, Anjul Patney, Hashim Sharif, \textbf{Yifan
Zhao}, Sarita Adve}

\cvpublist{[PPoPP'21]}
{ApproxTuner: A Compiler and Runtime System for Adaptive Approximations.}
{Hashim Sharif, \textbf{Yifan Zhao}, Maria Kotsifakou, Akash Kothari, Ben Schreiber,
Elizabeth Wang, Yasmin Sarita, Nathan Zhao, Keyur Joshi, Vikram Adve, Sasa Misailovic, Sarita Adve}

\cvpublist{[PLDI'19]}
{Huron: Hybrid False Sharing Detection and Repair.}
{Tanvir Ahmed Khan*, \textbf{Yifan Zhao}*, Gilles Pokam, Barzan Mozafari, Baris Kasikci}

\section{Teaching and Mentoring}

\subsection{Teaching Assistant}

\cvitem{Fall 2023}{UIUC CS 426 Compiler Construction (Sasa Misailovic)}
\cvitem{Fall 2018}{UMich CS 482 Operating Systems (Baris Kasikci)}

\subsection{Guest Lectures}

\cvitem{Fall 2023}{UIUC CS 426 Compiler Construction (2 tutorial lectures)}
\cvitem{Spring 2022}{UIUC CS 598 Approximate and Probabilistic Computing}
\cvitem{Fall 2021}{UIUC CS 526 Advanced Compiler Construction}

\subsection{Research Mentoring}

\cvshortlist{02/26 -- present}{UIUC undergraduate student, Aryan Agarwal and Sophia Baltz\newline{}
Collaborating to extend Neptune to new operators and improve scheduling.}
\cvshortlist{05/25 -- 12/25}{UIUC undergraduate student, Minsoo Kim\newline{}
Collaborated to extend Neptune to new hardware and operator setups.}
\cvshortlist{09/24 -- 01/25}{
  UIUC Undergraduate (IBM IIDAI program), Krish Patel and Vishesh Prasad\newline{}
Collaborated to improve the latency-prediction cost model used in Felix.}
\cvshortlist{08/22 -- 01/23}{UIUC Ph.D.~student, Vimarsh Sathia \newline{}
Collaborated on an extension of the ApproxCaliper project.}
\cvshortlist{12/20 -- 12/22}{UIUC undergraduate student, Peter Pao-Huang \newline{}
Collaborated on the ApproxCaliper project.}
\cvshortlist{12/21 -- 05/22}{UIUC undergraduate student, Yi Zhou \newline{}
Collaborated on an accuracy-aware tensor compiler project.}
\cvshortlist{05/21 -- 10/21}{Univ.~of Belgrade undergraduate student, Pavle
  Divovi\'c \newline{}
Collaborated on Tensor DSL, PyTorch backend in HPVM, and PyTorch performance portability.}

\section{Talks}

\textbf{Neptune}: Advanced ML Operator Fusion for Locality and Parallelism on GPUs
\begin{itemize}
  \item Compiler Seminar talk @ Illinois, 10/02/2025, University of Illinois
\end{itemize}

\textbf{Felix}: Optimizing Tensor Programs with Gradient Descent
\begin{itemize}
  \item ASPLOS'24 conference talk, 04/30/2024, San Diego
  \item Talk to IBM Compiler Team, 12/08/2023, Virtual
\end{itemize}

\textbf{ApproxCaliper}: Exploiting Application-level Error Resiliency for
Optimizing Neural Networks
\begin{itemize}
  \item MLSys conference talk, 06/06/2023, Miami Convention Center
  \item UIUC Compiler Seminar, 02/07/2022, University of Illinois
  \item Illinois Autonomous Farm Workshop, 07/07/2021, University of Illinois
\end{itemize}

\textbf{ApproxTuner}: A Compiler and Runtime System for Adaptive Approximations
\begin{itemize}
  \item Invited talk for a CS 598 (approx. computing) lecture, 03/10/2022, University of Illinois
  \item UIUC Visit Day Poster Session, 03/06/2022, University of Illinois
  \item Talk to Qualcomm Compiler Team, 12/13/2020, Virtual
  \item Talk to Amazon Compiler Team, 07/24/2020, Virtual
\end{itemize}

\section{Contributions to Research Grants}
\textit{Significantly contributed to writing of the proposals
that led to the following research grants being awarded:}

\textbf{Fellini: Differentiable ML Compiler for Full-Graph Optimization for LLM Models}
\begin{itemize}
  \item Amazon Research Award; PIs: Sasa Misailovic, Vikram S.~Adve; Apr.~2025.
  \item \$120k in cash funding and credits.
\end{itemize}

\textbf{Felix: Gradient-Based Compiler Optimization of Tensor Programs}
\begin{itemize}
  \item IBM-Illinois Discovery Accelerator Institute (IIDAI); PIs: Sasa Misailovic,
    Vikram S.~Adve; May 2023.
  \item Amount: \$500k.
\end{itemize}

\section{References}
\vspace{0.5em}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Sasa Misailovic} \newline{}
  Associate Professor \newline{}
  Siebel School of Computer Science, UIUC \newline{}
  misailo@illinois.edu
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Vikram Adve} \newline{}
  Donald B. Gillies Professor \newline{}
  Siebel School of Computer Science, UIUC \newline{}
  vadve@illinois.edu
\end{minipage}

\begin{minipage}[t]{0.5\textwidth}
  \vspace{1.5em}
  \textbf{Tianyin Xu} \newline{}
  Associate Professor \newline{}
  Siebel School of Computer Science, UIUC \newline{}
  tyxu@illinois.edu
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \vspace{1.5em}
  \textbf{Charith Mendis} \newline{}
  Assistant Professor \newline{}
  Siebel School of Computer Science, UIUC \newline{}
  charithm@illinois.edu
\end{minipage}

\end{document}
